Localisation and Sensor Privacy Using the Extended Information Filter and Secure Weighted Aggregation\thanksref{footnoteinfo}

### 2020-08-19 main.tex
Continued on aggregation section Added tikz image to show the aggregation protocol Moved the planned typiing of IND-CPA and AO games to the appendix Added some (to-be-moved later) tikz .tex files in the images folder

% User imported packages
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{algorithm}
\usepackage{algpseudocode}

@@

Section Summary

@@

\section{Problem Statement}

@@

\section{Private Weighted Aggregation Preliminaries}
% TODO define IND-CPA brielfy, AO and our version of AO *HERE* are reffer to it later

@@

In addition to encryption and decryption, the following homomorphic functions are provided by the Paillier scheme. $\forall m_1,m_2 \in \mathbb{Z}_n$,
\begin{align}
    \mathcal{D}(\mathcal{E}(m_1)\mathcal{E}(m_2)\pmod{n^2}) &= m_1+m_2\pmod{n} \\
    \mathcal{D}(\mathcal{E}(m_1)g^{m_2}\pmod{n^2}) &= m_1+m_2\pmod{n} \\
    \mathcal{D}(\mathcal{E}(m_1)^{m_2}\pmod{n^2}) &= m_1m_2\pmod{n}\,.
\end{align}

@@

When all encryptions $c_{i,t},\,i \in \{1,\dots,N\}$ are sent to the aggregator, private summation and decryption are computed by the functions
\begin{equation}
    c_{t} = H(t)^{sk_0}\prod^{N}_{i=1}c_{i,t} \pmod{n^2}
\end{equation}
and
\begin{equation}
    \sum^{N}_{i=1}m_{i,t} = \frac{c_{t}-1}{n}\,. \label{agg-decryption}
\end{equation}
Correctness follows from $\sum^{N}_{i=0}sk_i = 0$, and therefore
\begin{align}
    H(t)^{sk_0}\prod^{N}_{i=1}c_{i,t} \pmod{n^2} &\equiv H(t)^{sk_0}\prod^{N}_{i=1}(n+1)^{m_{i,t}} H(t)^{sk_i} \pmod{n^2} \\
    &\equiv H(t)^{\sum^N_{j=0}sk_j} \prod^{N}_{i=1}g^{m_{i,t}} \pmod{n^2} \\
    &\equiv (n+1)^{\sum^N_{i=1}m_{i,t}} \pmod{n^2}
\end{align}
which results in a solvable discrete logarithm by using \ref{agg-decryption}, as defined in \cite{joyeScalableSchemePrivacyPreserving2013}, with no more noise term.

@@

% Maybe rename this to Our Scheme or something like that
\section{Private Weighted Aggregation}
Explain it in as an overview

@@

\section{Private Localisation Preliminaries}

@@

\section{Private Localisation with Privacy-Preserving Sensors}
Explain it in as an overview. How is the aggregation scheme used, what does this require from the measurement model, why can this be a problem for normal distance sensors?

@@

\appendix
\section{A summary of Latin grammar}    % Each appendix must have a short title.
\section{Some Latin vocabulary}         % Sections and subsections are supported  
                                        % in the appendices.
\end{document}

>>>>

% User imported packages
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{tikz}
\usepackage{environ}
\usepackage{layouts}

\makeatletter
\newsavebox{\measure@tikzpicture}
\NewEnviron{scaletikzpicturetowidth}[1]{%
  \def\tikz@width{#1}%
  \def\tikzscale{1}\begin{lrbox}{\measure@tikzpicture}%
  \BODY
  \end{lrbox}%
  \pgfmathparse{#1/\wd\measure@tikzpicture}%
  \edef\tikzscale{\pgfmathresult}%
  \BODY
}
\makeatother

@@

Section Summary
%In Section \ref{sec:private_localisation} we will show how this scheme can be used to compute the measurement covariance and measurement vector homomorphically at each sensor, and allow the navigator to update their

@@

\section{Problem Statement} \label{sec:problem_statement}

@@

\section{Privacy-Preserving Weighted Aggregation}
For achieveing the goal of private localisation defined in Section \ref{sec:problem_statement} we require a cryptographic scheme which allows a time-series of homomorphically computed linear combinations of encrypted weights, to be summed by a privacy-preserving aggregation scheme. In our case, weights $\omega_1, \dots , \omega_m$ are encrypted and broadcast by the navigator, linear combinations $\sum^m_{j=1}x_{j,i}^{(t)}\omega_i$ are computed by the sensors $i \in \{1, \dots ,n\}$ at time $t$, and aggregation is computed back at the navigator. This has been summarized in Figure \ref{fig:agg_steps}. In Section \ref{sec:private_localisation} we will show how this scheme can be used to compute measurement covariances and measurement vectors homomorphically, and update the Extended Information Filter while preserving privacy.

\begin{figure}[htbp]
\centering
\vspace{\baselineskip}
\begin{tikzpicture}[scale=0.75]
    % Step 1
    \node at (5,22.5) {1. Broadcast and linear combinations step};
    % Navigator
    \node at (1.5,19.25) {\small Navigator};
    \fill (1.5,18.25) [blue!40] ellipse (0.5 and 0.5);
    % Sensors
    \node at (7.75,21.75) {\small Sensor $1$};
    \fill [red!40] (6.125,19.75) rectangle (9.375,21.25);
    \node at (7.75,20.5) {\small $\displaystyle y_1 = \sum^m_{i=1}x_{i,1}^{(t)}\omega_i$};
    \node at (7.75,14.75) {\small Sensor $n$};
    \fill [red!40] (6.125,15.25) rectangle (9.375,16.75);
    \node at (7.75,16) {\small $\displaystyle y_n = \sum^m_{i=1}x_{i,n}^{(t)}\omega_i$};
    \fill [black] (7.75,18.75) circle (0.05);
    \fill [black] (7.75,17.75) circle (0.05);
    \fill [black] (7.75,18.25) circle (0.05);
    % Lines
    \draw [-latex] plot[smooth, tension=.7] coordinates {(2,18.5) (6,20.25)};
    \draw [-latex] plot[smooth, tension=.7] coordinates {(2,18) (6,16.25)};
    \node at (4,20.25) {$(\omega_1,\dots ,\omega_m)$};
    \node at (4,16.25) {$(\omega_1,\dots ,\omega_m)$};

    % Step 2
    \node at (5,13.25) {2. Aggregation step};
    % Navigator
    \node at (3,10.75) {\small Navigator};
    \fill [blue!40] (0.625,8.75) rectangle (5.375,10.25);
    \node at (3,9.5) {\small $\displaystyle \sum^{n}_{j=1}\sum^{m}_{i=1} x_{i,j}^{(t)}\omega_i = \sum^n_{i=1}y^{(t)}_{i}$};
    % Sensors
    \node at (8.5,12.5) {\small Sensor $1$};
    \fill  (8.5,7.5) [red!40] ellipse (0.5 and 0.5);
    \node at (8.5,6.5) {\small Sensor $n$};
    \fill  (8.5,11.5) [red!40] ellipse (0.5 and 0.5);
    \fill [black] (8.5,10) circle (0.05);
    \fill [black] (8.5,9) circle (0.05);
    \fill [black] (8.5,9.5) circle (0.05);
    % Lines
    \draw [-latex] plot[smooth, tension=.7] coordinates {(8,11.25) (5.5,10)};
    \draw [-latex] plot[smooth, tension=.7] coordinates {(8,7.75) (5.5,9)};
    \node at (6.5,11.5) {$y_1$};
    \node at (6.5,7.5) {$y_n$};

    % Bounding rectangles
    \draw [gray] (0,23.25) rectangle (10,14.25);
    \draw [gray] (0,14) rectangle (10,5.5);
\end{tikzpicture}
\vspace{\baselineskip}
\caption{Required weighted aggregation scheme}
\label{fig:agg_steps}
\end{figure}

The security of a cryptographic scheme is typically defined by a security \textit{game}, which captures both the desired privacy guarantees, as well as the capabilities of attackers \cite{katzIntroductionModernCryptography2008}. Before defining the desired security of our scheme, we note that it has properties of both an additive homomorphic encryption scheme, and a privacy-preserving aggregation scheme. The typical security requirement for a homomorphic encryption scheme is Indistinguishability under the Chosen Plaintext Attack model (IND-CPA) \cite{}. Informally, IND-CPA states that an attacker who can choose plaintext messages to be encrypted at will, gains no additional information about an unkonwn plaintext message when they learn only its encryption. The more formal security game for IND-CPA has been given in Appendix \ref{app:ind-cpa}. Privacy-preserving aggregation, without weights, aims for the security goal of Aggregator Obliviousness (AO) \cite{}. AO states that no colluding subset of participants gains any additional information about the aggregation values from the remaining parties, given only their encryption, with the exception of learning only their sum if the aggregator is among the colluding subset. The game for AO has been given in Appendix \ref{app:ao}.

Our desired weighted aggregation method has two security goals. Firstly, that encrypted values are indistinguishable from random to sensors, and secondly, that individual weighted values remain unknown to the navigator, who learns only the final weighted sum. From the definitions above, it is clear that an IND-CPA secure encryption of navigator produced weights is sufficient for the first goal, while the definition of AO needs to be altered to incooporate weights for the second.

Such an altered aggregation games has been defined in \cite{alexandruEncryptedCooperativeControl2019} as private Weighted Sum Aggregator Obliviousness (pWSAO). In overview, the game states that given given weights --- not the case, need to define our own slightly different version (but we get to name it something else at least)

and is defined as follows

@@

In addition to encryption and decryption, the following homomorphic functions are provided by the Paillier scheme. $\forall m_1,m_2 \in \mathbb{Z}_n$,
\begin{align}
    \mathcal{D}(\mathcal{E}(m_1)\mathcal{E}(m_2)\!\pmod{n^2}) &= m_1+m_2\!\pmod{n} \\
    \mathcal{D}(\mathcal{E}(m_1)g^{m_2}\!\pmod{n^2}) &= m_1+m_2\!\pmod{n} \\
    \mathcal{D}(\mathcal{E}(m_1)^{m_2}\!\pmod{n^2}) &= m_1m_2\!\pmod{n}\,.
\end{align}

@@

When all encryptions $c_{i,t},\,i \in \{1,\dots,N\}$ are sent to the aggregator, private summation and decryption are computed by the functions
\begin{equation}
    c_{t} = H(t)^{sk_0}\prod^{N}_{i=1}c_{i,t} \pmod{n^2}
\end{equation}
and
\begin{equation}
    \sum^{N}_{i=1}m_{i,t} = \frac{c_{t}-1}{n}\,. \label{eqn:agg_decryption}
\end{equation}
Correctness follows from $\sum^{N}_{i=0}sk_i = 0$, and therefore
\begin{align}
    &H(t)^{sk_0}\prod^{N}_{i=1}c_{i,t} \pmod{n^2} \\
    \equiv &H(t)^{sk_0}\prod^{N}_{i=1}(n+1)^{m_{i,t}} H(t)^{sk_i} \pmod{n^2} \\
    \equiv &H(t)^{\sum^N_{j=0}sk_j} \prod^{N}_{i=1}g^{m_{i,t}} \pmod{n^2} \\
    \equiv &(n+1)^{\sum^N_{i=1}m_{i,t}} \pmod{n^2}
\end{align}
which results in a solvable discrete logarithm by using \eqref{eqn:agg_decryption}, as defined in \cite{joyeScalableSchemePrivacyPreserving2013}, with no more noise term.

@@

% Maybe rename this to Our Scheme or something like that
\section{Our Scheme}
Explain it in as an overview

@@

\section{Private Localisation}

@@

\section{Private Localisation with Privacy-Preserving Sensors} \label{sec:private_localisation}
Explain it in as an overview. How is the aggregation scheme used, what does this require from the measurement model, why can this be a problem for normal distance sensors?

@@

% Each appendix must have a short title.
% Sections and subsections are supported
% in the appendices.
\appendix
\section{Indistinguishability under the Chosen Plaintext Attack (IND-CPA)} \label{app:ind-cpa}
\section{Aggregator Obliviousness (AO)} \label{app:ao}

\end{document}
